Bayesian Nonparametric System Reliability\\ using Sets of Priors

### 2015-12-03 ijar-npb-ms.tex
minor changes in elicitation notes, more details for the n interval question

***Require $\yzu_{k,t_j} \ge \yzu_{k,t_{j+1}}$ and $\yzl_{k,t_j} \ge \yzl_{k,t_{j+1}}$.
If we know, e.g., pretty much what's going on for low $t$
but want to be much more cautious for high $t$,
then $\yktzl$ can drop to 0, but $\yktzu$ cannot increase.
Better to express certainty of prior guess via $\nktz$ bounds?
With strongly differing $\nktz$ values, it could however happen that, e.g., $\yzu_{k,t_j} \le \yzu_{k,t_{j+1}}$!
So require same $\nktz$ bounds for all $t$?
%(Prior guess for $p^k_t$ interpretation would say that $\yktz$ cannot increase,
%but does this need to hold for the prior guess range bound $\yktzu$?)***

***generally require $\yktzl > 0$ and $\yktzu < 1$ for all $t \not\in \big(\min(\vec{t}^k), \max(\vec{t}^k)\big)$
to get proper posteriors!?!***

@@

***we should also cover the case where $\yktz$ bounds are not given for all $t \in {\cal T}$,
as it will be too time-consuming to elicit $\yktz$ bounds for all $t$ in a dense grid.
(Calculating $\Rsys(t)$ for a too coarse grid only will waste information from data.)
Idea: ``fill up the $t$ grid at all $t$'' with least-committal bounds, i.e.: 
at all $t$ not elicited, take $\yktzu$ equal to last (in time sequence) elicited $\yktzu$,
and $\yktzl$ equal to next (in time sequence) elicited $\yktzl$.

>>>>

***Require $\yzu_{k,t_j} \ge \yzu_{k,t_{j+1}}$ and $\yzl_{k,t_j} \ge \yzl_{k,t_{j+1}}$.
If we know, e.g., pretty much what's going on for low $t$
but want to be much more cautious for high $t$,
then $\yktzl$ can drop to 0, but $\yktzu$ cannot increase.

***Better to express certainty of prior guess via $\nktz$ bounds?\\
With (strongly) differing $\nktz$ values, it can happen that, e.g., $\ynu_{k,t_j} < \ynu_{k,t_{j+1}}$!\\
E.g., when $\yzu_{k,t_j} = \yzu_{k,t_{j+1}}$ and $\yzl_{k,t_j} = \yzl_{k,t_{j+1}}$,
$s^k_t/n_k \in [\yzl_{k,t_j}, \yzu_{k,t_j}]$ (so no prior-data conflict) and no failures in $[t_j, t_{j+1}]$,\\
then with $\nzu_{k,t_j} < \nzu_{k,t_{j+1}}$ we have $\ynu_{k,t_j} < \ynu_{k,t_{j+1}}$,\\
 and with $\nzu_{k,t_j} > \nzu_{k,t_{j+1}}$ we have $\ynl_{k,t_j} > \ynl_{k,t_{j+1}}$.\\
(weighted average between interval and precise value: the lower $n$, the 'faster' the interval will shrink!)\\
So we need to require same $\nktz$ bounds for all $t$!
%(Prior guess for $p^k_t$ interpretation would say that $\yktz$ cannot increase,
%but does this need to hold for the prior guess range bound $\yktzu$?)***

***generally require $\yktzl > 0$ and $\yktzu < 1$ for all $t \not\in \big(\min(\vec{t}^k), \max(\vec{t}^k)\big)$
to get proper posteriors***

@@

***elicitation: we should also consider the case where $\yktz$ bounds are not given for all $t \in {\cal T}$,
as it will be too time-consuming to elicit $\yktz$ bounds for all $t$ in a dense grid.
(Calculating $\Rsys(t)$ for a too coarse grid only will waste information from data.)
Idea: ``fill up the $t$ grid at all $t$'' with least-committal bounds, i.e.: 
at all $t$ not elicited, take $\yktzu$ equal to last (in time sequence) elicited $\yktzu$,
and $\yktzl$ equal to next (in time sequence) elicited $\yktzl$.
